### 2022-07-04 letter.tex
Update content

\documentclass[11pt]{letter}
\usepackage[sfdefault]{noto}
\topmargin=-1in
\textheight=10in
\oddsidemargin=-10pt
\textwidth=6.5in
\date{yyyy-mm-dd}
\let\raggedleft\raggedright
\raggedbottom
\signature{myname}

\begin{document}
\begin{letter}{
theirname \\
theirtitle \\
theircompany \\
theirstreet1 \\
theirstreet2 \\
theircity\ \ theirstate\ \ \ \ theirzip
}

myname \\
mytitle \\
mystreet1 \\
mystreet2 \\
mycity~ mystate~~ myzip \\
phone \\
email

>>>>

\documentclass[11pt]{letter}
\usepackage[sfdefault]{noto}
\topmargin=-1in
\textheight=10in
\oddsidemargin=-10pt
\textwidth=6.5in
\date{yyyy-mm-dd}
\let\raggedleft\raggedright
\raggedbottom
\signature{myname}
\begin{document}
\begin{letter}{
theirname \\
theirtitle \\
theircompany \\
theirstreet1 \\
theirstreet2 \\
theircity\ \ theirstate\ \ \ \ theirzip \\
their phone \\
their email
}

myname \\
mytitle \\
mystreet1 \\
mystreet2 \\
mycity~ mystate~~ myzip \\
myphone \\
myemail
